Nested Sampling with Multiple Objective Functions

### 2018-06-15 doc/ms.tex
Infinity
Fixed walter reference

The combination of the reps makes use of the (approximate?) unbiasedness
property of Nested Sampling when the prior weights of the dead particles are
assigned proportional to
$[(N-1)/N]^i$ at iteration $i$, instead of being based on
Skilling's geometric sequence of $X$-values given by $\exp(-i/N)$.
\citet{walter} demonstrated that the Nested Sampling estimator of $Z$
is unbiased with these weights, but assuming perfect sampling of the replacement
particles at each iteration. Additionally, using the framework of
Sequential Monte Carlo \citep{doucet2001introduction},
\citet{salomone2018unbiased} showed that this remains true even if imperfect
MCMC is used to generate new particles. Technically, this property is
lost if the sequence of distributions is chosen adaptively (a key feature of NS)
rather than being fixed in advanced. However, this paper demonstrates that the
algorithm works well in practice despite this limitation.

@@

The first distribution is the prior $\pi(\xx)$. Objective function thresholds
$(\ell_1, \ell_2)_0 = (-\inf, -\inf)$ are assigned.
$N$ particles are generated
from the prior. Then, an objective function is selected according to the
probabilities $\{p_k\}$. Suppose the objective function chosen is number $k$.
Then the worst particle wrt that criteron is written to disk and replaced,
and the threshold is updated in the $k$th position only.

Essentially, a `rep' is just Nested Sampling, but where a threshold is
maintained for all objective functions. At each iteration, the space is
restricted by only one of the objective functions.

>>>>

The combination of the reps makes use of the (approximate?) unbiasedness
property of Nested Sampling when the prior weights of the dead particles are
assigned proportional to
$[(N-1)/N]^i$ at iteration $i$, instead of being based on
Skilling's geometric sequence of $X$-values given by $\exp(-i/N)$.
\citet{walter2017point} demonstrated that the Nested Sampling estimator of $Z$
is unbiased with these weights, but assuming perfect sampling of the replacement
particles at each iteration. Additionally, using the framework of
Sequential Monte Carlo \citep{doucet2001introduction},
\citet{salomone2018unbiased} showed that this remains true even if imperfect
MCMC is used to generate new particles. Technically, this property is
lost if the sequence of distributions is chosen adaptively (a key feature of NS)
rather than being fixed in advanced. However, this paper demonstrates that the
algorithm works well in practice despite this limitation.

@@

The first distribution is the prior $\pi(\xx)$. Objective function thresholds
$(\ell_1, \ell_2)_0 = (-\infty, -\infty)$ are assigned.
$N$ particles are generated
from the prior. Then, an objective function is selected according to the
probabilities $\{p_k\}$. Suppose the objective function chosen is number $k$.
Then the worst particle wrt that criteron is written to disk and replaced,
and the threshold is updated in the $k$th position only.

Essentially, a `rep' is just Nested Sampling, but where a threshold is
maintained for all objective functions. At each iteration, the space is
restricted by the value of only one of the objective functions.
